Interisland movements and oceanic swimming of woodland caribou in Newfoundland

### 2020-05-15 paper/manuscript.Rmd
tweak Q1

1) How do the energetic cost and risk of swimming differ from walking on sea
ice? Walking over solid ice is likely less energetically expensive than
swimming, but may pose a greater risk of falling through depending on the
thickness and stability of ice. What proportion of inter-island movements are
swimming events compared to walking on ice? Although the presence and extent of sea ice
varies annually,  we
deduce that although the majority of inter-island movements occur between April
1 and December 31, some inter-island movements appear to be caribou walking on
sea ice between islands (Figure 2B). Future research on the trade-offs of these types of
movement should consider both how the costs associated with each differ, but
also how the potential benefits - foraging opportunities - may vary seasonally.

>>>>

1) How do energetic costs and risks of swimming differ from walking on sea ice?
Walking over ice is less energetically expensive than swimming, but may pose a
greater risk of mortality from falling through the ice. Although the presence
and extent of sea ice varies annually,  we deduce that although the majority of
inter-island movements occur between April 1 and December 31, some inter-island
movements appear to be caribou walking on sea ice between islands (Figure 2B).
Our aim for future research on the trade-offs of these types of movement
considers how the costs, e.g. energy expenditure or mortality, and benefits,
e.g. novel foraging opportunities, may vary seasonally.
